---
title: "order_forecasting_random_forest"
output: html_document
date: "2024-08-09"
---

# Random Forest

```{r, setup}
# Set up
library(mlbench)
library(tidymodels)
library(DALEX)
library(ranger)
library(Rcpp)
library(corrplot)
library(ggplot2)
library(gridExtra)
library(SHAPforxgboost)
library(lubridate)
lst_csv = list.files(pattern = '.csv')

# Read all csv files in the directory and save as df with the same name of the file
for (i in lst_csv){
  temp_df = read.csv(i)  
	assign(gsub('.csv','',i),temp_df)}


train_df = train %>% 
  select(-c(holiday_name, id, shutdown, mini_shutdown, blackout, mov_change, frankfurt_shutdown, precipitation, snow, user_activity_1, user_activity_2)) %>% 
  mutate(date = as.Date(date)) %>% 
  mutate(weekdays = wday(date)) 

test_df = test %>% 
  mutate(date = as.Date(date)) %>% 
  mutate(weekdays = wday(date)) 
```


```{r}
split = initial_split(train_df, 0.8)
rf.train = training(split)
rf.test = testing(split)

model = rand_forest(trees = 500, min_n = 15, mtry = 7) %>% 
  set_engine(engine = "ranger", seed(6)) %>% 
  set_mode("regression")

fit = model %>% 
  fit(orders ~., data = rf.train)
fit
```
500 , 0.9655295

```{r}
result = rf.test %>% 
  select(orders) %>% 
  bind_cols(predict(fit, rf.test))

metrics = metric_set(yardstick::rmse, yardstick::rsq, yardstick::mape)

result %>% 
  metrics(orders, .pred)
```


```{r}
test_result = bind_cols(result, rf.test)
ggplot(test_result, aes(x=date, y=.pred, color=warehouse)) +
  geom_line() +
  labs(title="Prediction",
       x="Date",
       y="Value") +
  theme_minimal()

ggplot(test_result, aes(x=date, y=orders...1, color=warehouse)) +
  geom_line() +
  labs(title="Acctual",
       x="Date",
       y="Value") +
  theme_minimal()
```

```{r}
# Creating a plot
plot <- ggplot(test_result, aes(x = orders...1, y = .pred, color = warehouse)) +
  geom_point(aes(shape = warehouse), size = 3) +  # Using points with shapes by group
  geom_line(aes(group = warehouse), linetype = "dashed") +  # Connecting points with lines within groups
  geom_abline(intercept = 0, slope = 1, linetype = "solid", color = "gray") +  # Adding a 45-degree line
  labs(x = "Actual Value", y = "Predicted Value", title = "Comparison of Actual and Predicted Values by Group") +
  theme_minimal() +
  scale_color_brewer(type = 'qual', palette = "Set1")  # Color settings

# Display the plot
print(plot)

```

Base Plot: Set up using ggplot with actual values on the x-axis and predicted values on the y-axis.
Points: Added using geom_point() where shapes can be assigned based on groups.
Lines: geom_line() with dashed lines connects the points within each group to show trends.
45-degree Line: geom_abline() adds a reference line where perfect predictions would lie.
Aesthetics: labs() sets labels and titles, theme_minimal() gives a clean theme, and scale_color_brewer() assigns distinct colors for different groups.



```{r}
explainer = fit %>% 
  explain(
    data = rf.test %>% select(-orders),
    y = test$orders
  )
```


```{r}
shap = explainer %>% 
  predict_parts(
    new_observation = rf.test %>% dplyr::slice(11),
    type = "shap",
    B = 25)
plot(shap)

```


```{r}
prediction = as.data.frame(predict(fit, test_df)) %>% 
  mutate( id = test_df$id) %>% 
  mutate( warehouse = test_df$warehouse) %>% 
  mutate( date = test_df$date) %>% 
  rename( orders = .pred)
```


```{r}
ggplot(prediction, aes(y = orders, x = date, color = as.factor(warehouse)))  +
  geom_line() +
  labs(title="Prediction",
       x="Date",
       y="Value") +
  theme_minimal()
```

```{r}
prediction = merge(solution_example, prediction, by = "id") %>% 
  select(-c(orders.x, date, warehouse))
```


```{r}
write.csv(prediction, 'prediction_15_random_forest.csv',row.names = FALSE)
```



